Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-19 writing/embedded_meta_learning_appendix.tex
Anonymized
Organization & numerical results with all runs

\appendix

\section{Detailed methods} \label{app_detailed_methods}
\subsection{Datasets}
\subsubsection{Polynomials} \label{meth_data_poly}
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant from all the variables.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par
\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
\begin{itemize}
\item Classifying polynomials as constant/non-constant.
\item Classifying polynomials as zero/non-zero intercept.
\item For each variable, identifying whether that variable was relevant to the polynomial.
\end{itemize}
We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
\begin{itemize}
\item Squaring polynomials (where applicable).
\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
\end{itemize}
\textbf{Language:} We encoded the meta-tasks in language by sequences as follows:
\begin{itemize}
\item Classifying polynomials as constant/non-constant: \verb|[``is'', ``constant'']|
\item Classifying polynomials as zero/non-zero intercept: \verb|[``is'', ``intercept_nonzero'']|
\item For each variable, identifying whether that variable was relevant to the polynomial: \verb|[``is'', <variable-name>, ``relevant'']|
\item Squaring polynomials: \verb|[``square'']|
\item Adding a constant: \verb|[``add'', <value>]|
\item Multiplying by a constant: \verb|[``multiply'', <value>]|
\item Permuting inputs: 
\begin{verbatim}[``permute'', <variable-name>, <variable-name>, <variable-name>, 
<variable-name>]\end{verbatim}
\end{itemize}
All sequences were front-padded with ``<PAD>'' to the length of the longest sequence.

@@

\subsection{Source repositories}
The full code for the experiments and analyses can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
%%(will be made available in the de-anonymized version.)
\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

\section{Supplemental figures}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
\caption{The system is able to infer polynomials from only seeing a few data points (i.e. evaluations of the polynomial), despite the fact that during training it always saw 50. A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
\label{supp_poly_sweep_results}
\end{figure}

@@

\section{Lesion experiments}

@@

\subsection{Polynomials}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
EML & Trained & 0.014 & 0.011 & 0.017 \\
EML & Held out & 0.218 & 0.153 & 0.291 \\
Untrained EML network & Trained & 5.735 & 4.787 & 6.787 \\
Untrained EML network & Held out & 5.968 & 4.967 & 6.975 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
\hline \\[-1.8ex] 
EML & Trained mapping, on trained task & 0.084 & 0.08 & 0.088 \\ 
EML & Trained mapping, on held-out task & 1.664 & 1.345 & 2.077 \\ 
EML & Held-out mapping, on trained task & 1.07 & 0.996 & 1.14 \\ 
EML & Held-out mapping, on held-out task & 1.52 & 1.444 & 1.604 \\ 
Untrained EML network & Trained mapping, on trained task & 13.378 & 12.213 & 14.84 \\ 
Untrained EML network & Trained mapping, on held-out task & 15.469 & 13.778 & 17.303 \\ 
Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.766 & 8.687 \\ 
Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.165 & 9.127 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
\end{table}

>>>>

\appendix
The supplemental material is organized as follows: in section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses. In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain. In section \ref{app_supp_figures} we provide supplemental figures. In section \ref{app_lesion_results} we provide some lesion studies. In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper. 
\section{Detailed methods} \label{app_detailed_methods}
\subsection{Datasets}
\subsubsection{Polynomials} \label{meth_data_poly}
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant from all the variables.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random coefficient drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par
\textbf{Meta-tasks:} For meta-tasks, we trained the network on 6 task-embedding classification tasks:
\begin{itemize}
\item Classifying polynomials as constant/non-constant.
\item Classifying polynomials as zero/non-zero intercept.
\item For each variable, identifying whether that variable was relevant to the polynomial.
\end{itemize}
We trained on 20 meta-mapping tasks, and held out 16 related meta-mappings.
\begin{itemize}
\item Squaring polynomials (where applicable).
\item Adding a constant (trained: -3, -1, 1, 3, held-out: 2, -2).
\item Multiplying by a constant (trained: -3, -1, 3, held-out: 2, -2).
\item Permuting inputs (trained: 1320, 1302, 3201, 2103, 3102, 0132, 2031, 3210, 2301, 1203, 1023, 2310, held-out: 0312, 0213, 0321, 3012, 1230, 1032, 3021, 0231, 0123, 3120, 2130, 2013).
\end{itemize}
\textbf{Language:} We encoded the meta-tasks in language by sequences as follows:
\begin{itemize}
\item Classifying polynomials as constant/non-constant: \verb|[``is'', ``constant'']|
\item Classifying polynomials as zero/non-zero intercept: \verb|[``is'', ``intercept_nonzero'']|
\item For each variable, identifying whether that variable was relevant to the polynomial: \verb|[``is'', <variable-name>, ``relevant'']|
\item Squaring polynomials: \verb|[``square'']|
\item Adding a constant: \verb|[``add'', <value>]|
\item Multiplying by a constant: \verb|[``multiply'', <value>]|
\item Permuting inputs: 
\begin{verbatim}[``permute'', <variable-name>, <variable-name>, <variable-name>, 
<variable-name>]\end{verbatim}
\end{itemize}
All sequences were front-padded with ``<PAD>'' to the length of the longest sequence.

@@

\subsection{Source repositories}
The full code for the experiments and analyses can be found on github:
%%\begin{itemize}
%%\item \url{https://github.com/lampinen/polynomials}
%%    \begin{itemize}
%%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
%%    \end{itemize}
%%\item \url{https://github.com/lampinen/meta_cards} 
%%\end{itemize}
(will be made available in the de-anonymized version.)
\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

\section{Supplemental figures} \label{app_supp_figures}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/basic_results_sweeping.png}
\caption{The system is able to infer polynomials from only seeing a few data points (i.e. evaluations of the polynomial), despite the fact that during training it always saw 50. A minimum of 15 random points is needed to correctly infer polynomials without prior knowledge of the polynomial distribution, but the system is performing well below this value, and quite well above it, although it continues to refine its estimates slightly when given more data.}
\label{supp_poly_sweep_results}
\end{figure}

@@

\section{Lesion experiments} \label{app_lesion_results}

@@

\subsection{Polynomials}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
EML & Trained & 0.015 & 0.012 & 0.018 \\
EML & Held out & 0.246 & 0.188 & 0.308 \\
Untrained EML network & Trained & 5.735 & 4.823 & 6.74 \\
Untrained EML network & Held out & 5.968 & 4.984 & 6.991 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
EML & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
EML & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
EML & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
EML & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
Untrained EML network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
Untrained EML network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
Untrained EML network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
Untrained EML network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
\end{table}
